---
title: Stock Report
date: today
date-format: long
published-title: produced
format: email
attachments:
  - data.csv
email-preview: true
---

## Report for TSLA

```{r, echo=TRUE, message=FALSE}
library(DT)
library(formattable)
library(ggthemes)
library(quantmod)
library(dplyr)
library(plotly)
library(xts)

prices <- round(getSymbols("TSLA", auto.assign = FALSE, src = "yahoo"), 2)
close <- Cl(xts::last(prices))
open <- Op(xts::last(prices))

recent <- xts::last(prices, n = 90)

prices_df <- prices %>%
  as_tibble() %>%
  mutate(
    Date = index(prices), 
    Direction = ifelse(TSLA.Close >= TSLA.Open, 'Increasing', 'Decreasing')
  )
```

The stock closed `r ifelse(close>open,'up','down')` at `r close` dollars per share yesterday.

### Price History

The chart below is made with the `quantmod` and `plotly` R packages. An API returns all of the price history based on the stock tick symbol "TSLA.".


```{r build_plot, echo=TRUE, warning=FALSE, message=FALSE}
fig1 <- plot_ly(prices_df) %>%
  add_trace(
    type = "candlestick", x = ~Date, name = "TSLA",
    open = ~TSLA.Open, close = ~TSLA.Close,
    high = ~TSLA.High, low = ~TSLA.Low,
    increasing = list(line = list(color = '#17BECF')),
    decreasing = list(line = list(color = '#7F7F7F'))
  ) %>% 
  layout(yaxis = list(title = "Price"))

fig2 <- plot_ly(prices_df) %>%
  add_bars(
    x = ~Date, y = ~TSLA.Volume, name = "TSLA Volume",
    color = ~Direction, colors = c('#17BECF', '#7F7F7F')
  ) %>%
  layout(yaxis = list(title = "Volume"), xaxis = list(title = ""))

subplot(
  fig1, fig2, heights = c(0.7, 0.2), nrows = 2,
  shareX = TRUE, titleY = TRUE
) %>%
  layout(
    hovermode = "x", margin = list(t = 80),
    title = paste("Tesla from", min(prices_df$Date), "to", max(prices_df$Date)),
    xaxis = list(
      rangeselector = list(
        x = 0, y = 1, xanchor = 'left', yanchor = "top",
        visible = TRUE, font = list(size = 9),
        buttons = list(
          list(count = 1, label = 'RESET', step = 'all'),
          list(count = 1, label = '1 YR', step = 'year', stepmode = 'backward'),
          list(count = 3, label = '3 MO', step = 'month', stepmode = 'backward'),
          list(count = 1, label = '1 MO', step = 'month', stepmode = 'backward')
        )        
      )
    ),
    legend = list(
      x = 1, y = 1, xanchor = 'right',
      orientation = 'h', font = list(size = 10)
    )
  )
```

### Raw Data

The table below displays the daily price data for the stock. A concise, interactive table is created with the `DT` package. 

  
```{r show_data, echo=TRUE}
recent %>%
  as_tibble() %>%
  mutate(TSLA.Volume = TSLA.Volume / 1000000) %>%
  datatable() %>%
  formatCurrency(c("TSLA.Open", "TSLA.High", "TSLA.Low", "TSLA.Close"), digits = 2) %>%
  formatRound("TSLA.Volume", digits = 0)
```

## Legacy Information

This report also produces a CSV file containing recent price data, which may
be used in other analysis.

```{r write_csv, echo = FALSE, include = FALSE}
write.csv(recent, file = "data.csv")
```

[Link to CSV](data.csv)

## Email

This report also produces an email that is sent to key stakeholders with summary
information. 

::: {.email}

```{r compute_subject, warning = FALSE, message = FALSE, echo = FALSE}
# Calculate the total change
close <- Cl(xts::last(prices, n = 2))
diff <- round(as.numeric(close[2]) - as.numeric(close[1]), 2)
subject <- sprintf("TSLA is %s today by $%g!", 
        ifelse(diff > 0,"up", "down"), 
        abs(diff))

# ideally, we would always compute the email content but 
# suppress its scheduled sending only when (abs(diff) > 0.5)
```

::: {.subject}
`r#subject`
:::

# Stock Update

Hello Team,

Here are the latest stock prices for **TSLA** as of `r Sys.Date()`:

```{r, echo = FALSE}
price_new <- prices[, c(1, 4)]
colnames(price_new) <- c("open", "close")
price_new$change <- price_new$close - price_new$open

# include a table with the stock prices
format_table(
    x = as.data.frame(tail(price_new)),
    list(
      change = formatter(
        "span",
        style = x ~ ifelse(
          x > 0, 
          formattable::style(color = "green"),
          formattable::style(color = "red")))
    )
  )
```

The historical trend is shown below: 

```{r, echo = FALSE, message = FALSE}
# include a plot with the price data
recent[, 6] %>%
  autoplot() +
  geom_smooth() +
  theme_fivethirtyeight() +
  labs(
    title = sprintf("%s Price Adjusted", "TSLA")
  )
```

Let me know if you have any questions.

Best,

Team Lead

:::

